\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lastpage}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headheight}{14pt}
\renewcommand{\footskip}{10pt}

% Set \headrulewidth to 0pt to remove the underline
\renewcommand{\headrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

%%%%%%%% Date automatically updates
\newcommand{\nowdate}{\today}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{fancy}

\fancyfoot{}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}

% I changed the link color, not a huge fan of cyan.
\hypersetup{colorlinks,breaklinks,
            urlcolor=[rgb]{0.0,0.0,0.0},
            linkcolor=[rgb]{0,0,0}}

\begin{document}
    \pagestyle{fancy}
    \thispagestyle{fancy}
    
    \begin{center}
        {\LARGE{\bf{Dong-geon Lee}}\\}
    \end{center}
    
    \vspace{-14pt}
    
    %----------HEADING-----------------
    \begin{center} 
        {\href{mailto:lee.dg.125@gmail.com}{lee.dg.125@gmail.com} \\}
        {
            ( \underline{\href{https://github.com/oneonlee}{GitHub}}, 
            \underline{\href{https://www.linkedin.com/in/dong-geon-lee/}{LinkedIn}} )
        }
    \end{center}

    %----------Research Interests-----------------
    \section{\\Research Interests}
    \begin{enumerate}[noitemsep, leftmargin=*,label={}]
    \item{ Deep learning, Natural language processing, Semi-supervised learning}
    \end{enumerate}
    
    %-----------Education-----------------
    \section{Education}
    \begin{itemize}[leftmargin=*,label=]
        \resumeSubheading
        {\textbf{B.S.} in \textbf{\href{http://bit.ly/3Uu4LTi}{Information and Communication Engineering}}}{March 2018 - Present}{\href{https://eng.inha.ac.kr/eng/index.do}{Inha University}}{Incheon, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Expected Graduation Date: February 16, 2024}
                \item{GPA: 3.77 / 4.5}
                \item{Relevant Coursework: \textit{AI Applications, Data Structure, Algorithm Capstone Design, \\ Signals and Systems, Database Capstone Design, Object Oriented Programming}}
            \end{itemize}
    \end{itemize}
    
    %---------------Research Experiences---------------------------
    \section{Research Experiences}
    \begin{itemize}[leftmargin=*,label=]
        \resumeSubheading
        {\textbf{Research Assistant} (Advisor: \underline{\href{http://bit.ly/3zSrQ8F}{Prof. Wonik Choi}})}{November 2022 - Present}
            {\href{http://dilab.inha.ac.kr/}{Data Intelligence Laboratory}, Inha University}{Incheon, South Korea}
        \resumeSubheading
        {\textbf{Research Assistant} (Advisor: \underline{\href{http://bit.ly/412nYOw}{Prof. Insook Cho}})}{August 2021 - June 2023}
            {Nursing Informatics Laboratory, Inha University}{Incheon, South Korea}
    \end{itemize}
    
    %---------------Projects---------------------------
    \section{Projects}
    \begin{itemize}[leftmargin=*,label=]
        \resumeSubheading
        {\textbf{Big Data-Driven Aviation Safety Management Technology}}{November 2022 - Present}
            {\href{http://dilab.inha.ac.kr/}{Data Intelligence Laboratory}, Inha University}{Incheon, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Development of keyphrase extraction model through semi-supervised learning}
            \end{itemize}
        \resumeSubheading
        {\textbf{FallSafe: Reducing Falls with Clinical Data}}{August 2021 - June 2023}
            {Nursing Informatics Laboratory, Inha University}{Incheon, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Development of deep learning-based fall statement detection model}
                \item{Development of NER model for automatic fall report generation}
                \item{Network analysis for drug prescription patterns}
            \end{itemize}
        \resumeSubheading
        {\textbf{Intelligent Clinical Guidance System Development}}{August 2021 - December 2021}
            {Nursing Informatics Laboratory, Inha University}{Incheon, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Topic-modeling for insightful medical data analysis}
            \end{itemize}
        \resumeSubheading
        {\textbf{Smart Port Traffic Control System}}{April 2021 - November 2021}
            %{ICT Mentoring, The Federation of Korean Information Industries}{Seoul, South Korea}
            {ICT Mentoring, Ministry of Science and ICT}{Sejong, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Development of a deep learning-based system for real-time detection of parking conditions}
                \item{Development of a real-time lane recognition algorithm through image processing}
            \end{itemize}
    \end{itemize}
    
    %---------------Conferences---------------------------
    \section{Conferences}
    \begin{enumerate}[noitemsep, leftmargin=*,label={[\arabic*]}]
        \item {Insook Cho, EunJu Lee, and \textbf{Dong-geon Lee}. Effects of Language Differences on Inpatient Fall Detection Using Deep Learning. \textit{MedInfo 2023: The 19th World Congress on Medical and Health Informatics}, Sydney, July 2023. (Poster)}
        
        \item {\textbf{Dong-geon Lee}, EunJu Lee, and Insook Cho. Bridging the Reporting Gap of Inpatient Falls to Improve Safety Practices Using Deep-Learning-Based Language Models and Multisite Data. \textit{AMIA 2023 Clinical Informatics Conference}, Chicago, United States, May 2023. (Peer Reviewed, Oral Presentation)}
        
        \item {\href{https://doi.org/10.3745/PKIPS.y2021m11a.1342}{Changhun Koo*, Yoonjoo Jung*, and \textbf{Dong-geon Lee*}. Through deep learning-based video processing, Design and implementation of Smart Port Parking Information System. In \textit{Proceedings of the Annual Conference of KIPS 2021}, Yeosu, South Korea, November 2021. (Oral Presentation, *: Co-First Author)}}
    \end{enumerate}
    
    %---------------Teaching Experiences---------------------------
    \section{Teaching Experiences}
    \begin{itemize}[leftmargin=*,label=]
        \resumeSubheading
        {\textbf{Teaching Assistant} of \textbf{ICE1005: Introduction to AI Programming}}{Spring 2023}
            {Dept. of Information and Communication Engineering, \href{https://eng.inha.ac.kr/eng/index.do}{Inha University}}{Incheon, South Korea}
        \resumeSubheading
        {\textbf{Teaching Assistant} of \textbf{ICE3020: Algorithm Capstone Design}}{Spring 2023}
            {Dept. of Information and Communication Engineering, \href{https://eng.inha.ac.kr/eng/index.do}{Inha University}}{Incheon, South Korea}           
        \resumeSubheading
        {\textbf{Computer Programming Instructor} (Part-time)}{October 2021 - May 2023}
            {\href{https://jamcoding.co.kr/}{Jamcoding, Co., LTD}}{Seoul, South Korea}
            \begin{itemize}[label=\bullet]
                \item{Courses: \textit{Data Analysis and Visualization, Programming and Algorithms (Python \& C)}}
            \end{itemize}
    \end{itemize}

    %---------------Technical Skills---------------------------
    \section{Technical Skills}
    \begin{enumerate}[noitemsep, leftmargin=*,label=]
        \item{
            \begin{itemize}[label=\bullet]
                \item{\textbf{Programming Languages}: Python, C++, C, JavaScript}
                \item{\textbf{Frameworks and Libraries}: PyTorch, Keras, TensorFlow, KoNLPy, OpenCV}
                \item{\textbf{Systems and Tools}: Git, Linux, MySQL, AWS, Arduino, \LaTeX}
            \end{itemize}
        }
    \end{enumerate}
    
    %-----------Certifications-----------
    \section{Certifications}
    \begin{enumerate}[noitemsep, leftmargin=*,label={[\arabic*]}]
        \item{\textbf{\href{https://user-images.githubusercontent.com/73745836/216896341-f17186c1-7883-4dc6-b2a5-5063e2fc5e80.jpeg}{Deep Learning Course (Advanced)}}. \textit{\href{http://fvt.inha.ac.kr/}{Inha Innovation Sharing University for Future Vehicle Technology}}, January 2023.}
                
        \item{\textbf{\href{https://courses.nvidia.com/certificates/3635de0b089446bb8e95c101b05518e4/}{Building Transformer-Based Natural Language Processing Applications}}}. \textit{\href{https://www.nvidia.com/en-us/training/}{NVIDIA Deep Learning Institute}}, August 2022.}
        
        \item{\textbf{\href{https://courses.nvidia.com/certificates/825e75c11f3541fa9c196832ffa1db8d/}{Fundamentals of Deep Learning}}. \textit{\href{https://www.nvidia.com/en-us/training/}{NVIDIA Deep Learning Institute}}, August 2022.}
        
        \item{\textbf{\href{https://user-images.githubusercontent.com/73745836/163787775-86eb9285-5eeb-4539-aed0-0fb977c102ff.jpg}{Amazon Web Services (AWS) Machine Learning Course}}. \textit{\href{http://fvt.inha.ac.kr/}{\href{https://user-images.githubusercontent.com/73745836/163787768-c1565a01-57f1-41e0-a436-44a214caaa38.jpg}{Inha Innovation Sharing University for Future Vehicle Technology}}}, February 2022.}
        
        \item{\textbf{\href{https://user-images.githubusercontent.com/73745836/163787768-c1565a01-57f1-41e0-a436-44a214caaa38.jpg}{Understanding Deep Learning}}. \textit{Hancom Academy}, February 2022.}
    \end{enumerate}
    

    %---------------Patent---------------------------
    \section{Patent}
    \begin{enumerate}[noitemsep, leftmargin=*,label={[\arabic*]}]
        \item{System for providing parking information and control method. \textit{KR-Application No. 10-2021-0178090}, South Korea, December 2021.}
    \end{enumerate}

    %---------------Language Skills---------------------------
    \section{Language Skills}
    {\textbf{Advanced level of English proficiency} demonstrated by a TOEIC score of 805 obtained in February 2023.} 

\end{document}
%-------------------------------------------